Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-05 Multiresolution_framework/ltx/manuscript.tex
minor edits

To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters. In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e. $T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small. Data is generated using the connectivity kernel composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape (see Fig.\ref{fig:KernelEstimate}) given by

@@

	w(r-r')=200\times N_{4;1,-3}(r-r')-100\times N_{4;0,-3}(r-r')

>>>>

To demonstrate the performance of the MRAIDE estimation framework, data was generated synthetically  using Eqs.~\eqref{eq:DiscreteTimeModel} and \eqref{eq:ObservationEquation}, allowing a comparison between true and estimated parameters. In doing so, the membrane time constant was set to $\tau = 10$~ms \citep{David2003}, and the sampling time was chosen ten times faster \citep{Stephan2008}, i.e. $T_s = 1$~ms, ensuring the discrepancy between the continuous neural field model and its discrete approximation is small. The connectivity kernel used for data generation composed of two B-spline scaling functions at $j=0$ and $j=1$ forming a compact support Mexican hat shape (see Fig.\ref{fig:KernelEstimate}) given by

@@

	w(r-r')=200\times N_{4;1,-3}(r-r')-100\times N_{4;0,-3}(r-r').
